%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=ResumeBlue, linkcolor=ResumeBlue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\definecolor{ResumeBlue}{RGB}{20, 110, 200}
\definecolor{ResumeGray}{RGB}{162,162,165}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{ResumeBlue}
}{}{0em}{}[\color{ResumeBlue}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \color{ResumeGray}#2 \\
      \textit{\small#3} & \color{ResumeGray}\textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gokulbarath SK} \\ \vspace{2pt}
    \small Chennai, India $|$ \href{mailto:gokul00060@gmail.com}{\underline{gokul00060@gmail.com}} $|$ 
    \href{https://gokulbarath.is-a.dev}{\underline{gokulbarath.is-a.dev}} \\ \vspace{2pt}
    \small GitHub: \href{https://github.com/gokul6350}{\underline{gokul6350}} $|$ LinkedIn: \href{https://linkedin.com/in/gokulbarath}{\underline{gokulbarath}}
\end{center}


%-----------PROFILE-----------
\section{Profile}
    \small{Passionate AI and ML developer dedicated to building intelligent systems and agentic workflows. Third-year Mechatronics Engineering student with hands-on experience in Large Language Models (LLMs), Model Context Protocol (MCP), and software integration. Focused on developing practical, AI-powered tools that leverage modern frameworks to solve complex problems through intelligent automation.}
    
    \vspace{2pt}
    \small{\textbf{Total 64 GitHub Stars} across all repositories}
    \vspace{7pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sathyabama Institute of Science \& Technology}{Chennai, India}
      {Bachelor of Engineering in Mechatronics Engineering}{June 2023 -- May 2027}
    \resumeSubheading
      {Bright International School}{Ahmedabad, Gujarat}
      {Higher Secondary Education (CBSE)}{2021 -- 2023}
    \resumeSubheading
      {Delhi Public School}{Gandhinagar, Gujarat}
      {Secondary Education (CBSE)}{Mar. 2021}
  \resumeSubHeadingListEnd


%-----------OPEN SOURCE-----------
\section{Open Source Contributions}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{LangChain} $|$ \href{https://github.com/gokul6350?tab=overview\&org=langchain-ai}{\emph{Ecosystem Contributor}}}{}
      \resumeItemListStart
        \resumeItem{Identified missing Groq vision support (issue \#34589) and authored PR \#2259 in langchain-ai/docs, adding the complete Vision + multimodal section (now live in official docs). Enables seamless adoption of vision-capable models like Llama-4 Scout/Maverick.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Deep Shell} $|$ \emph{Python, CLI Development, NLP} $|$ 27 Stars}{\href{https://gokulbarath.is-a.dev/\#projects}{GitHub}}
          \resumeItemListStart
            \resumeItem{Intelligent terminal application that uses natural language processing to interpret and execute shell commands.}
            \resumeItem{Features integrated chat interface enabling users to interact with their system using conversational AI.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{GNX CLI} $|$ \emph{Python, Groq, Large Language Models}}{\href{https://github.com/gokul6350/gnx-cli}{GitHub}}
          \resumeItemListStart
            \resumeItem{Developed a Next-Gen AI Agent that goes beyond text to control Desktop and Android environments.}
            \resumeItem{Implements a modular, agentic architecture where a main controller drives memory retrieval and tool execution.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{EduVid-LLM} $|$ \emph{Python, Generative AI, LLMs}}{\href{https://gokulbarath.is-a.dev/\#projects}{GitHub}}
          \resumeItemListStart
            \resumeItem{Designed a planning-centric architecture for automated educational video generation.}
            \resumeItem{Leverages LLMs to transform educational content into structured video scripts and visual assets.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
    \vspace{-5pt}
    \small{Additional projects available at: \href{https://gokulbarath.is-a.dev/\#projects}{\underline{gokulbarath.is-a.dev/\#projects}}}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Artificial Intelligence \& ML}{: Large Language Models (LLMs), Model Context Protocol (MCP), Agentic Workflows, Diffusion Models, OpenCV, Reinforcement Learning, PyTorch, TensorFlow} \\
     \textbf{Programming Languages}{: Python, C/C++, JavaScript, TypeScript, Bash Scripting} \\
     \textbf{Software Development}{: FastAPI, Flask, Next.js, React.js, Tailwind CSS, Git, SQL, Shell Scripting} \\
     \textbf{Languages}{: English (Fluent), Tamil (Native), Hindi (Fluent), Gujarati (Fluent)}
    }}
 \end{itemize}


%-----------CERTIFICATIONS-----------
\section{Certifications \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Introduction to Deep Learning} -- Kaggle Learn \hfill Feb. 2024 \\
     \textbf{CS50’s Introduction to Artificial Intelligence with Python} -- Harvard University \hfill Aug. 2023 
    }}
 \end{itemize}


\end{document}
